A thesis draft

### 2018-12-04 thesis/res/sections/10-ProjectAnalysis.tex
Add presentation and fix travis

\subsubsection{Docker Swarm}
\label{chap:prjan:sec:tech:sub:other:sub:swarm}
Introduced in 2014~\cite{swarmGit}, Docker Swarm allows multiple Docker nodes to
cluster together and be seen as one logical unit. This layer completely makes
the underlying infrastructure transparent: data management, as network one, are
totally managed by Docker. Recently, Docker-compose support has been introduced,
making this one-node tool available for clustered systems. At the end of the
day, on one hand Docker Swarm provides an easy way to set up a cluster system
with all the tools configured out-of-the-box, without the necessity to set
networking configurations or installing ad-hoc storage solutions. On the other
hand, though, it does not have all the customization options that Kubernetes
offers, thus making the product less flexible. This fundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.

@@

>>>>

\subsubsection{Docker Swarm}
\label{chap:prjan:sec:tech:sub:other:sub:swarm}

@@

Introduced in 2014~\cite{swarmGit}, Docker Swarm allows multiple Docker nodes to
cluster together and be seen as one logical unit. This layer completely makes
the underlying infrastructure transparent: data management, as network one, are
totally managed by Docker. Recently, Docker-compose support has been introduced,
making this one-node tool available for clustered systems. At the end of the
day, on one hand Docker Swarm provides an easy way to set up a cluster system
with all the tools configured out-of-the-box, without the necessity to set
networking configurations or installing ad-hoc storage solutions. On the other
hand, though, it does not have all the customization options that Kubernetes
offers, thus making the product less flexible. This fundamental characteristic,
although, makes the two solutions have different use cases leading to different
market needs.
